Loop-Aware Optimizations in PyPy's Tracing JIT

### 2011-06-17 talk/iwtc11/paper.tex
a para about warming up (and a bench file in-progress)
started to draft abstract

\begin{abstract}
This is the text of the abstract.
\end{abstract}

@@

>>>>

\begin{abstract}
By introducing loop peeling into the optimization step of a tracing
jit, the effect of optimizations already in place will be increased
greatly. Not only will they become able to move loop invariant code
out of loop. They will also become able to reuse results from the
previous iteration. Also, the implementation of excising optimizations
can be left almost intact as they will not have to interact much with
the loop peeling.

Several benchmarks executed on the PyPy python JIT show over 2
times increase in speed when loop peeling was introduced. This makes
some of them almost match optimized C performance and become over XXX
times faster than cpython.
\end{abstract}

@@

For all JITted run (PyPy and Psyco) 3 iterations were run to warm up the JIT,
followed by 10 iterations for averaging. For GCC and CPython, 5 iterations
were run. In all cases, the standard deviation is very low, making benchmarks
very well reproducible.
